---
title: "Us_murders_Rmarkdown"
author: "sahilkaushik93"
date: "11/7/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# load the library tidyverse to perform some fuctions :
```{r}
library(tidyverse)
```

# load the data of US murders by FBI :

```{r}
load("rda/murders.rda")
```

# wrangling the data and segregating the output by region :

```{r}
murders <-read_csv("data/murders.csv")
murders <- murders %>% mutate(region = factor(region),rate = total / population * 10^5)
save(murders,file = "rda/murders.rda")
```


## Including Plots

You can also embed plots, for example:

```{r, echo=FALSE}
murders %>% mutate(abb= reorder(abb,rate)) %>% 
  ggplot(aes(abb,rate)) +
  geom_bar(width = 0.5,stat = "identity",color="Yellow")+
  coord_flip()

ggsave("figs/barplot.png")
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

# Key points :
The knitr package is used to compile R markdown documents.
The first time you click the "knit" button on the editor pane a pop-up window will prompt you to install packages, but after that is completed, the button will automatically knit your document.
github_document gives a .md file, which will give the best presentation on GitHub

# To change the type of output :
output: html_document 
output: pdf_document 
output: word_document
output: github_document





